Halo alignments with large scale tidal and velocity fields

### 2013-02-19 paper/main.tex
outlines

\section{The algorithms}
\label{sec:algorithms}

@@

\subsection{Volume and Mass filling fractions}

@@

>>>>

... There is abundant literature on the issue of shape and angular momentum
aligmnent of dark matter haloe with respect to the cosmic we.

... This alignment is often measured from the distribution of the
$\cos\theta$ where $\theta$ is the angle between the two axes of
interest.

... Table 1 summarizes recent results found in the literature for
shape and angular momentum alignment.

\section{N-body simulation and halo finding}

... In this paper we use groups found with a FOF halo finder.

\section{The cosmic web algorithms}
\label{sec:algorithms}

\subsection{The Tidal Web}

\subsection{The Velocity Web}

\subsection{Numerical considerations}

... In this paper we compute the cosmic web on grids of two different
resolutions $256^3$ and $512^3$.

@@

@@

...
